---
title: "Hw05"
output: github_document
---

Welcome to Hw05!!!

# I am going to work on the task **Make API queries “by hand” using httr**

For this purpose I am going to work with the Game of Thrones API called *Ice And Fire* which you can find [here](https://anapioficeandfire.com/).
The overall limit is 20k per Ip Adress.
Data format is JSON

# Loading libraries

```{r,message=FALSE,warning=FALSE}
library(tidyverse)
library(jsonlite)
library(purrr)
library(tibble)
library(ggplot2)
library(forcats)
library(glue)
```



## The overall process

- I first extracted the data for "Stark of Winterfell" family.
    - Here I am using **"FromJSON"** as the data is in JSON format (API - https://anapioficeandfire.com/api/houses/362)


```{r}
Stark <- fromJSON("https://anapioficeandfire.com/api/houses/362")
```

List of Members URL

```{r}
head(Stark$swornMembers,10)
```


- Then I created a tibble with First variable House name, next House Members name, next his Gender, next Tv series he is in, next Books he is in.
    - For this the family have sub list named members where the API's for all other members are listed
    - I then directly used these API's without making changes as they were exact, and created a tibble with first column House name and information about each member by again using **"FromJASON"** and map (Purrr) and named Mem_info.
    - Then I created another columns named Name (chr), Gender(chr), Books(list),TvSeries (list) from the data of Mem_info.

A Function which return list with name y from the list x

```{r}
Infor <- function(x,y="name"){
	if (y=="name"){
		unlist(x$name)
	} else if(y=="gender"){
		unlist(x$gender)
	} else if(y=="tvSeries"){
		sub(".*Season ","",unlist(x$tvSeries))
	} else if(y=="books"){
		sub(".*books/","",unlist(x$books))
	}
}
```
    
Creating the tibble
    
```{r}
Stark_info <- tibble(House=Stark$name,Mem_info=map(Stark$swornMembers,fromJSON),Name=map2(Mem_info,"name",Infor),Gender=map2(Mem_info,"gender",Infor),Books=map2(Mem_info,"books",Infor),TvSeries_Seas=map2(Mem_info,"tvSeries",Infor)) %>% select(House,Name,Gender,TvSeries_Seas,Books) 
```
    
A glimpse of tibble

```{r}
knitr::kable(head(Stark_info,10))
```


- Now I plotted how many males and females are there in each house (bar graph)

```{r}
Total_females <- nrow(Stark_info %>% filter(Gender=="Female"))
Total_Males <- nrow(Stark_info %>% filter(Gender=="Male"))
Pop <- data_frame(Gender=c("Stark_Males","Stark_Females"),Pop=c(Total_Males,Total_females))
ggplot(Pop,aes(x=Gender,weight=Pop)) + geom_bar(aes(fill=Gender))+labs(title="Female stark vs Male Stark") + theme(plot.title = element_text(hjust=0.5))
```


- I also plotted how many characters from this house were there in each season and each book (Bar Graph)

**EACH SEASON**

Function returns a list of true and false for each "1" to "y" in the character array x 

```{r}
ret <- function(x,y){
	a=c()
	for (i in 1:y){
		a=cbind(a,as.character(i) %in% unlist(x))
	}
	return(a)
}
```
**First unlisted the list got from map and then created a matrix with 6 rows with each column representing a charatcter and each row a season and took transpose.**
**Then created a tibble and plotted them**

```{r}
All_char_all_seas <- t(matrix(unlist(unlist(map2(Stark_info$TvSeries_Seas,6,ret))),nrow = 6))
```

Glimpse of matrix

```{r}
head(All_char_all_seas,10)
```

Plot here on

```{r}
Char_seas <- tibble(Seasons = c("S1","S2","S3","S4","S5","S6"),Char_count=colSums(All_char_all_seas))

ggplot(Char_seas,aes(x=Seasons,weight=Char_count)) + geom_bar(aes(fill=Seasons))+labs(title="Stark characters per season") + theme(plot.title = element_text(hjust=0.5))
```

**EACH BOOK**

**First unlisted the list got from map and then created a matrix with 11 (as 11 books) rows with each column representing a charatcter and each row a book and then took transpose.**
**Then created a tibble and plotted them**

```{r}
All_char_all_books <- t(matrix(unlist(unlist(map2(Stark_info$Books,11,ret))),nrow = 11))
```

Glimpse of matrix

```{r}
head(All_char_all_books,10)
```

Plot here on

```{r}
Ordering <- c("B1","B2","B3","B4","B5","B6","B7","B8","B9","B10","B11")
Char_seas <- tibble(Books=Ordering,Char_count=colSums(All_char_all_books))

ggplot(Char_seas,aes(x=fct_reorder(Books,c(1:11)),weight=Char_count)) + geom_bar(aes(fill=Books))+labs(title="Stark characters per book") + theme(plot.title = element_text(hjust=0.5)) + scale_x_discrete("Books")
```

- Next I took each book and plotted number of characters in each book (bar graph)
     - I got the data usinf **fromJSON** on the following [APIs](https://anapioficeandfire.com/api/books/10)
     - The format is again JSON 

- First I made a tibble with column Books having books from 1 to 11
- Next I mutated Information about each book using glue, map and fromJSON 

```{r}
Ordering <- c("1","2","3","4","5","6","7","8","9","10","11")
book_data <- tibble(Books = Ordering)
book_data <- book_data %>% mutate(data=map(glue("https://anapioficeandfire.com/api/books/{Books}"),fromJSON))
```

- Next I mutated another column named Tcharacters which is total sum of characters in each book
- Removed the data column
    
```{r}
book_data_comp <- book_data %>% mutate(Tcharacters = unlist(map(data,function(x){length(x$characters)}))) %>% select(-data)
```
    
Glimpse of tibble

```{r}
knitr::kable(book_data_comp)
```

Plotting the number of characters in each book

```{r}
ggplot(book_data_comp,aes(x=fct_reorder(Books,c(1:11)),weight=Tcharacters)) + geom_bar(aes(fill=Books))+labs(title="Total characters per book") + theme(plot.title = element_text(hjust=0.5)) + scale_x_discrete("Books")
```

## Saving data for future use

```{r}
saveRDS(Stark_info,"Stark_family.rds")
saveRDS(book_data_comp,"Book_char_details.rds")
```


    